Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-26 paper/section-general-framework.tex
Tiny fixes

\paragraph{Relational interpretation of primitive types.}
Having fixed a model
% $\mathcal{M}$ 
we next choose a relational interpretation 
%$\mathcal{R}$ 
of
primitive types: for each each primitive type
$\tyPrimNm{X}$, a relational interpretation parameterised by elements
from the model: $\semPrimType{\tyPrimNm{X}} :
\semSort{\primTyArity(\tyPrimNm{X})} \to \Rel(\tyPrimSem{\tyPrimNm{X}})$.

>>>>

\paragraph{Relational interpretation of primitive types.}
Having fixed a model
% $\mathcal{M}$ 
we next choose a relational interpretation 
%$\mathcal{R}$ 
of
primitive types: for each each primitive type
$\tyPrimNm{X}$, its relational interpretation is parameterised by elements
from the model: $\semPrimType{\tyPrimNm{X}} :
\semSort{\primTyArity(\tyPrimNm{X})} \to \Rel(\tyPrimSem{\tyPrimNm{X}})$.
